Inferring the gravitational potential of the Milky Way with a few precisely measured stars

### 2014-02-12 text/paper2/ms.tex
more refs and text

The difficulty and computational costs associated with proper N-body modeling has motivated numerous efforts for developing approximate methods for constraining properties of the Galactic potential with cold debris structures.

% Generate approx. to N-body -> single Orbit --> Orbits + offsets --> Bovy
% method, problem, etc. then address what we fix

- Broader comparison to other methods\\
\indent\indent- 'generative methods' more generally (ie N-body, Bovy, plus Varghese, plus Kuepper plus new possible action-angle models....\\
\indent\indent- Sanders \& Binney 2013\\
\indent\indent- statistical methods, Penarrubia, Sanderson, Rewinder\\
- Then a short note on worries\\
\indent\indent- for generative models\\
\indent\indent- for any methods based on action/angle \\
\indent\indent- GD-1 was fit as if it highlighted an orbit.  That is known to be wrong.\\
\indent\indent- Densities are hard to match: need a background model, way to go from luminosity to density, needs assumptions about the mass function and structure of the satellite\\
\indent\indent- Triaxiality / radially-dependent shapes and substructure present problems for integral-based methods\\
- Then how rewinder gets round these????\\
\indent\indent- Reference Deg \& Widrow to say they illustrate the idea of the power of multiple streams to back up the bit where you say that's the long-term aim\\

>>>>

The difficulty and computational costs associated with proper N-body modeling has motivated numerous efforts for developing approximate methods for constraining properties of the Galactic potential with cold debris structures. The simplest approximation is to fit a single orbit to observed debris \citep[e.g.,][]{koposov10, deg13}. This has the advantage of naturally incorporating observational errors, but is known to be invalid as debris does not exactly follow an orbit \citep[e.g.,][]{binney08, eyre11, sanders13a}. To account for this, methods have been proposed that model the debris as an orbit plus some dispersion or offset in phase space \citep[e.g.,][]{eyre09a, varghese11, kuepper12} and action-angle coordinates \citep{eyre11, sanders13b, bovy14}. Other statistical methods have been proposed \citep[][]{penarrubia12, sanderson14} that may prove powerful when applied to, e.g., data from the \gaia mission, where full 6D coordinates will be known for large samples of stars in the halo --- and therefore many debris structures --- but membership is not necessarily known. However, these methods do not account for observational errors.

In methods that rely on action-angle coordinates, [...].

- Then a short note on worries\\
\indent\indent- for generative models\\
\indent\indent- for any methods based on action/angle \\
\indent\indent- GD-1 was fit as if it highlighted an orbit.  That is known to be wrong.\\
\indent\indent- Densities are hard to match: need a background model, way to go from luminosity to density, needs assumptions about the mass function and structure of the satellite\\
\indent\indent- Triaxiality / radially-dependent shapes and substructure present problems for integral-based methods\\
- Then how rewinder gets round these????\\
\indent\indent- Reference Deg \& Widrow to say they illustrate the idea of the power of multiple streams to back up the bit where you say that's the long-term aim\\
